---
title: "STA426 Week 1"
author: "thomasfischer42"
date: "18 9 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(gridExtra)
```


# Week 1 part b)

1. Acquaint yourself with knitR PDF/HTML Rmarkdown documents.

2. Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. (In general, do not just dump the R code and plots in the HTML document; break your exercises into sections with headings, add some text and make it readable.

## Draw samples from log-normal distribution
```{r}
n <- 100
mu <- 1
sd <- 0.5

set.seed(2019)
x <- rlnorm(n, mu, sd)
y <- rnorm(n, mu, sd)
```


## Set up visualisations
```{r}
# Histogram
p_hist <- ggplot() +
  geom_histogram( aes( x = x)) + 
  theme_minimal()

# Density on log scale
p_dens <- ggplot() + 
  geom_density( aes(x = log(x))) + 
  geom_density( aes(x = y), lty = 2, col = "red") + 
  theme_minimal()
```


## Plot visualisations
```{r}
gridExtra::grid.arrange(p_hist, p_dens)
```

The histogram is strongly right-skewed.  

The red line represents the density of a sample drawn from $N(0,1)$, whereas the black line corresponds to the log transformed log-normal sample. They're relatively similar in terms of location and shape. 

## Using inline chunks

The sample mean is `r round(mean(x), 3)`, and the sample variance is `r round(var(x), 3)`. 
